Audio-based multi-level music structure analysis using deep learning

### 2023-01-14 MasterThesis.tex
Template update
Third update

%Title parameters
\title{Multi-level audio-based music structure analysis}
\author{Oriol Colomé Font}
\submitdate{July 2023}
\supervisor{Carlos Lordelo and Carl Thomé}
\cosupervisor{Frederic Font}

@@

\maketitle
\restoregeometry

>>>>

%Title parameters
\title{Audio-based multi-level music structure analysis using deep learning}
\author{\href{oriol.colome.font@epidemicsound.com}{Oriol Colomé Font}}
\submitdate{July 2023}
\supervisor{Carlos Lordelo and Carl Thomé}
\cosupervisor{Frederic Font}

\hypersetup{
pdftitle={Your PDF title},
pdfsubject={Your PDF subject},
pdfauthor={Oriol Colomé Font},
pdfkeywords={Music Information Retrieval; Music Structure Analysis; Deep Learning}
}

@@

%\maketitle
\restoregeometry

### 2023-01-14 acknowledgements/acknowledgements.tex
Third update

\begin{acknowledgement}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
(Optional, if used, placed on a right page next to an empty left page)

I want to express my sincere gratitude to:

\begin{itemize}
 \item My supervisor
 \vspace*{3mm}
 \item My co-supervisor
 \vspace*{3mm}
 \item My family
 \vspace*{3mm}
\end{itemize}

>>>>

\begin{acknowledgement}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)

\begin{itemize}
\item I want to express my sincerest gratitude to Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis. Your expertise in MIR helped shape the direction of my research and make it a success. Your unwavering support and encouragement helped me overcome any difficulties I encountered during the process. I also appreciate the time and effort you invested in mentoring me. Your dedication to your students is truly inspiring, and I am honored to have had the opportunity to work with you.
\vspace*{3mm}
\item My co-supervisor
\vspace*{3mm}
\item The Music Technology Group (MTG)
\vspace*{3mm}
\item I would also like to thank my colleague and superior at My Sheet Music Transcriptions, Oriol López, for his exceptional support and flexibility throughout my thesis. His understanding and willingness to accommodate my academic commitments effectively allowed me to balance my work and research responsibilities. His guidance and advice on professional matters have been instrumental in my growth as a professional. I am genuinely grateful for his unwavering support and encouragement and for being a great mentor.
\vspace*{3mm}
Thank you all for being excellent advisors and playing a crucial role in completing my thesis. I sincerely appreciate everything you have done for me and will always cherish the knowledge and experience I have gained under your guidance.
\vspace*{3mm}
\item My family
\vspace*{3mm}
\item My girlfriend
\vspace*{3mm}
\end{itemize}

### 2023-01-14 introduction/introduction.tex
Third update

MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other fields. It can be applied to various musical styles and genres and has been used for tasks such as music transcription, music generation, and music similarity. \cite{rodriguez2005bilateral}
\section{Motivation}

>>>>

The fundamental concept behind MSA is the ability to divide a song into distinct, non-overlapping segments, assigning a label to each segment that defines its type. This segmentation and labeling process aims to capture a human's perception or analysis of the song.

MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other fields. It can be applied to various musical styles and genres and has been used for tasks such as music transcription, music generation, and music similarity.

%\cite{rodriguez2005bilateral}

\section{Motivation}

In preview work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and performance \cite{Nieto2020}. Additionally, we have examined the primary challenges that MSA currently faces, particularly in regards to subjectivity, ambiguity, and hierarchy.
